### 2020-01-23 overview.tex
summary rough

\thesisstructure
In the remaining of \emph{Part I}, an extended overview on droplet interactions and suspension flow is summarized from previous studies in the literature.
In Chapter \ref{chp:micro-hydro}, we formulate the microhydrodynamics mathematically and spotlight the essential physics for one, two and more particles in various flow or geometries. These are the prerequisites for understanding droplet interactions in more complicated conditions.
In Chapter \ref{chp:num-methods}, we introduce two categories of numerical methodologies that either solve the governing equations directly or approximate the solution in reduced order. Each category is then divided into several classes, which have further variantions and are mentioned succinctly.
These are followed by a short detour in Chapter \ref{chp:misc}, where two additional topics that are studied alongside the main subject are also described.
Finally, Chapter \ref{chp:summary} concludes the first part of the thesis, and \emph{Part II} contains the original results.

@@

>>>>

\thesisstructure
In the remaining of \emph{Part I}, an extended overview on droplet interactions and suspension flow is summarized from previous studies in the literature.
In Chapter \ref{chp:micro-hydro}, we formulate the microhydrodynamics mathematically and spotlight the essential physics for one, two and more particles in various flow fields or geometries. These are the prerequisites for understanding droplet interactions in more complicated conditions.
In Chapter \ref{chp:num-methods}, we introduce two categories of numerical methodologies that either solve the governing equations directly or approximate the solution in reduced order. Each category is then divided into several classes, which have further variantions and are mentioned succinctly.
These are followed by a short detour in Chapter \ref{chp:misc}, where two additional topics studied alongside the main subject are motivated and described.
Finally, Chapter \ref{chp:summary} concludes the first part of the thesis, leading to \emph{Part II} where the original results are collected.

@@

The investigations presented in this thesis are motivated by the interest in understanding droplet interactions and suspension flow that originates from a number of applications, including material science, microfluidic technology and transport of complex fluids.
The general physical picture and underlying mathematical formulation are described in Chapter \ref{chp:micro-hydro}, where we introduce the elementary properties of the Stokes flow and its approximate solutions in the presence of liquid droplets or solid particles in a few simple cases.
These are the fundamentals of microhydrodynamics, essential for building a physical intuition and making back-of-the-envelope estimates when faced with more complicated engineering problems.
Unfortunately, sometimes a problem may be too complicated to be solved analytically, or we may simply be misguided by our intuitions.
In those cases, numerical simulations offer a relatively inexpensive means to visualise fluid motions and disentangle the various effects.
Therefore, Chapter \ref{chp:num-methods} provides a mini-review of some currently popular methods that can be applied to simulate coupled multiphase systems.
This is the main subject of the present work -- we develop methods, implement algorithms, and simulate droplets or particles in fluids to reproduce experiments or verify theories.
The specific aim may differ by applications; what remains the same is the numerical approach to problem solving as well as a curiosity-driven effort to uncover more physical principles.

\begin{figure}%[b]
  \centering
  \includegraphics[width=0.95\columnwidth]{paper-diagram.pdf}
  \caption{Diagrammatic representation of the papers in Part II parameterized by the number of droplets ($N$) that are or could potentially be studied, and by the distance (indicated by color) to being purely experimental ($-1$) or purely theoreticaly ($1$); 0 corresponds to purely numerical. Note that \emph{Paper 6} does not have a meaningful definition of $N$.}
  \label{fig:p-diagram}
\end{figure}

The detailed results of the present work are given in the next part of the thesis in the format of journal articles or technical reports.
Among them, 
Papers 1--4 entail droplet interactions,
Papers 5 \& 6 are miscellaneous, and
Paper 7 concerns suspension flow.
Separate summaries of each paper are given in the beginning of Part II.
A diagrammatic categorization is also illustrated in Figure \ref{fig:p-diagram}.
Overall, the common limitation of the conducted studies is the lack of a simple quantitative model that predicts the main phenomenon.
It is quite often the case that weak qualitative conclusions are drawn from the simulations, and a new set of simulations may have to be performed in very different conditions.

Finally, as a outlook to future studies, lessons learned from the present thesis include:
(i) Flow-assisted droplet assembly for photonic crystals is not straightforward. Perhaps disorder materials.
(ii) Level set methods are mass-leaking; not recommended for solving engineering problems for its own sake. But it is still fun to develop methods and it may have other applications, such as modelling tissue growth.
(iii) IB simulations for particle interactions are very slow. Patience.
(iv) Droplets in turbulence is an exciting new avenue, a lot to simulate and model.
(v) Wetting is important but nasty.
(vi) Dense suspension is very exciting, many parameters to do, very interesting from a theoretical point of view, also can be a testbed for new methods.

### 2020-01-23 paper1/paper.tex
summary rough

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[ICLS/GFM for droplet suspensions under depletion forces] % Short title used in headlines (optional)
{%
  An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces} % Title for toc
%
\paperauthor[Ge, Loiseau, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Jean-Christophe Loiseau, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, J-Ch. Loiseau, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[J. Comput. Phys.] % Short publish info used in List Of Papers
{%
	Journal of Computational Physics%
}%
%
\papervolume{353}%
%
\papernumber{}%
%
\paperpages{435--459}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this first work, I developed and implemented an interface-correction level set/ghost fluid method (\texttt{ICLS/GFM}) for high-fidelity simulations of liquid droplets in an immiscible carrier fluid. The main novelty is a global mass correction scheme, which is conceptually easy to understand, relatively straightforward to program, and fast if implemented properly. The method works best for well-resolved droplets as validated in the paper; however, extra care must be taken when applying it otherwise. In the same paper, I also formulated a hydrodynamic model for surfactant-induced depletion forces between neighbouring drops, removing the need to simulate suspending surfactants, hence further improving the computational efficiency. The overall methodology can be readily used to study droplet interactions in liquid flows, and may be extended to simulate multiphase flows in porous media in general.
}%
%
\graphicspath{{paper1/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[ICLS/GFM for droplet suspensions under depletion forces] % Short title used in headlines (optional)
{%
  An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces} % Title for toc
%
\paperauthor[Ge, Loiseau, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Jean-Christophe Loiseau, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, J-Ch. Loiseau, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[J. Comput. Phys.] % Short publish info used in List Of Papers
{%
	Journal of Computational Physics%
}%
%
\papervolume{353}%
%
\papernumber{}%
%
\paperpages{435--459}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this first work, we developed and implemented an interface-correction level set/ghost fluid method (\texttt{ICLS/GFM}) for high-fidelity simulations of liquid droplets in an immiscible carrier fluid. The main novelty is a global mass correction scheme, which is conceptually easy to understand, relatively straightforward to program, and fast if implemented properly. The method works best for well-resolved droplets as validated in the paper; however, extra care must be taken when applying it otherwise. In the same paper, I also formulated a hydrodynamic model for surfactant-induced depletion forces between neighbouring drops, removing the need to simulate suspending surfactants, hence further improving the computational efficiency. The overall methodology can be readily used to study droplet interactions in liquid flows, and may be extended to simulate multiphase flows in porous media in general.
}%
%
\graphicspath{{paper1/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-01-23 paper2/paper.tex
summary rough

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Flow-assisted droplet assembly in a 3D microfluidic channel] % Short title used in headlines (optional)
{%
  Flow-assisted droplet assembly in a 3D microfluidic channel% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Flow-assisted droplet assembly in a 3D microfluidic channel} % Title for toc
%
\paperauthor[Ge, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Soft Matter.] % Short publish info used in List Of Papers
{%
	Soft Matter%
}%
%
\papervolume{15}%
%
\papernumber{}%
%
\paperpages{3451--3460}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this paper, I performed a series of simulations, using methods developed in \emph{Paper 1}, to examine the droplet interaction in increasingly realistic conditions, mimicking a microfluidic experiment. The main objective was to elucidate the physical mechanism that leads to the experimentally observed droplet clustering, which had been explained by a dipolar interaction theory. Contrary to previous belief, we found that dipolar interactions alone cannot account for the fast droplet dynamics; a number of 3D effects must be included to faithfully reproduce the observation. This conclusion is supported by theoretical derivations of the Stokes flow (\emph{Papers 3 \& 4}), implying that designing microfluidic channels to directly produce large droplet crystals remains difficult in practice.
}%
%
\graphicspath{{paper2/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Flow-assisted droplet assembly in a 3D microfluidic channel] % Short title used in headlines (optional)
{%
  Flow-assisted droplet assembly in a 3D microfluidic channel% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Flow-assisted droplet assembly in a 3D microfluidic channel} % Title for toc
%
\paperauthor[Ge, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Soft Matter.] % Short publish info used in List Of Papers
{%
	Soft Matter%
}%
%
\papervolume{15}%
%
\papernumber{}%
%
\paperpages{3451--3460}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this paper, we performed a series of simulations, using methods developed in \emph{Paper 1}, to examine the droplet interaction in increasingly realistic conditions, mimicking a microfluidic experiment. The main objective was to elucidate the physical mechanism that leads to the experimentally observed droplet clustering, which had been explained by a dipolar interaction theory. Contrary to previous belief, we found that dipolar interactions alone cannot account for the fast droplet dynamics; a number of 3D effects must be included to faithfully reproduce the observation. This conclusion is supported by theoretical derivations of the Stokes flow (\emph{Papers 3 \& 4}), implying that designing microfluidic channels to directly produce large droplet crystals remains difficult in practice.
}%
%
\graphicspath{{paper2/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-01-23 paper5/paper.tex
summary rough

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Droplets in homogeneous shear turbulence] % Short title used in headlines (optional)
{%
  Droplets in homogeneous shear turbulence% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Droplets in homogeneous shear turbulence} % Title for toc
%
\paperauthor[Rosti, Ge, Jain, Dodd, Brandt] % Short authors used in headlines and List Of Papers
{%
  Marco E. Rosti$^1$, Zhouyang Ge$^1$, Suhas S. Jain$^2$, \\Michael S. Dodd$^2$, Luca Brandt$^{1,3}$%
}%
%
\listpaperauthor{M.E. Rosti, Z. Ge, S.S. Jain, M.S. Dodd, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Center for Turbulence Research, Stanford University, CA 94305, USA\\%
  $^3$ Department of Energy and Process Engineering, Norwegian University of Science and Technology (NTNU), NO 7491, Norway%
}%
%
\paperjournal[J. Fluid Mech.] % Short publish info used in List Of Papers
{%
	Journal of Fluid Mechanics%
}%
%
\papervolume{876}%
%
\papernumber{}%
%
\paperpages{962--984}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This paper reports a simulation study of liquid droplets stirred in another immiscible  fluid under homogeneous shear turbulence at  a  shear  Reynolds  number  equal to  15 200. The flow and droplet statistics, including Taylor-microscale  Reynolds  numbers, turbulent  kinetic  energy budget, droplet size distributions, \textit{etc.}, were examined under various surface tensions and initial droplet diameters. The overall results suggest that the dispersed  phase acts  as  a  sink  of  the turbulent  kinetic  energy  for  the  carrier  fluid and the Hinze scaling for droplet sizes could apply even in the presence of droplet coalescence and a mean shear.
}%
%
\graphicspath{{paper5/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Droplets in homogeneous shear turbulence] % Short title used in headlines (optional)
{%
  Droplets in homogeneous shear turbulence% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Droplets in homogeneous shear turbulence} % Title for toc
%
\paperauthor[Rosti, Ge, Jain, Dodd, Brandt] % Short authors used in headlines and List Of Papers
{%
  Marco E. Rosti$^1$, Zhouyang Ge$^1$, Suhas S. Jain$^2$, \\Michael S. Dodd$^2$, Luca Brandt$^{1,3}$%
}%
%
\listpaperauthor{M.E. Rosti, Z. Ge, S.S. Jain, M.S. Dodd, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Center for Turbulence Research, Stanford University, CA 94305, USA\\%
  $^3$ Department of Energy and Process Engineering, Norwegian University of Science and Technology (NTNU), NO 7491, Norway%
}%
%
\paperjournal[J. Fluid Mech.] % Short publish info used in List Of Papers
{%
	Journal of Fluid Mechanics%
}%
%
\papervolume{876}%
%
\papernumber{}%
%
\paperpages{962--984}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This paper reports a simulation study of liquid droplets stirred in another immiscible  fluid under homogeneous shear turbulence at  a  shear  Reynolds  number  equal to  15 200. The flow and droplet statistics, including Taylor-microscale  Reynolds  numbers, turbulent  kinetic  energy budget, droplet size distributions, etc., were examined under various surface tensions and initial droplet diameters. The overall results suggest that the dispersed  phase acts  as  a  sink  of  the turbulent  kinetic  energy  for  the  carrier  fluid and the Hinze scaling for droplet sizes could apply even in the presence of droplet coalescence and a mean shear.
}%
%
\graphicspath{{paper5/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}
